An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-09 gas-adsorption/rsc-gas-ads-complete.tex
edits

\section{Flexible two-phase model}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Maximal possible deliverable capacity of methane in a two-phase, collapsing substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison, along with the free energy difference between open and closed conformations~\cite{mason2015methane}.}
    \label{fig:methane-flexible}
\end{figure}
Although our deliverable capacity limit does not directly apply to materials that change conformation in
response to gas adsorption, we can estimate enhancements in the deliverable capacity provided by
such materials. 
For example, consider a material such as Co(bdp) \cite{mason2015methane} that 
can, actuated by the presence of gas, switch between two distinct structural phases: 
an ``open'' phase where gas molecules can fit in the pore space and a 
collapsed, ``closed'' phase in which no gas can fit inside.

Let $\Delta F=F_{\text{open}}-F_{\text{closed}}$ be the Helmholtz free energy difference per mole of adsorbent between the two phases in the absence of gas.
Suppose the closed phase is more stable ($\implies \Delta F >0$), so that upon a reduction in the pressure of the gas, the material will collapse and expel all residual gas to enhance the deliverable capacity compared to rigid materials that will retain some gas at $\pempty$. 
In addition, we assume the open phase hosts a uniform, attractive potential energy field $\V<0$ for gas molecules to adsorb, so that eqn.~\ref{eq:xi_vs_xi0} holds for the open phase of the material.
In terms of $\rho_g(\mu, T)$, then, the grand potential $\Omega$ in our idealized substrate is:
\begin{equation}
    \Omega(T, \mu) = - \int_{-\infty}^\mu \rho_g(\mu-\V)d\mu.
\end{equation}
See Coudert et al. \cite{coudert2008thermodynamics}.
However, the \emph{osmotic potential}.
% David: introduce units of delta G here.

>>>>

\section{Flexible two-phase model}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{methane-298-flexible}
    \caption{Maximal possible deliverable capacity of methane in a two-phase, collapsing substrate at 298\ K as a function of the free energy difference 
      between open and closed phases. The experimental deliverable capacity for Co(bdp) is shown for
       comparison, along with the free energy difference between open and closed conformations~\cite{mason2015methane}.}
    \label{fig:methane-flexible}
\end{figure}
While our deliverable capacity limit does not apply to materials that change conformation in
response to gas adsorption, here we adapt our theoretical framework to pertain to bistable adsorbents modeled after Co(bdp) \cite{mason2015methane}.
Actuated by the presence of gas, Co(bdp) can switch between two distinct structural phases:
an ``open'' phase where gas molecules can fit in the pore space and a 
collapsed, ``closed'' phase in which no gas can fit inside.

We follow Coudert et al. \cite{coudert2008thermodynamics} in developing a thermodynamic model for a two-phase adsorbent. 
Let $\Delta F=F_{\text{open}}-F_{\text{closed}}$ be the Helmholtz free energy difference per mole of adsorbent between the two phases in the absence of gas.
Suppose the closed phase is more stable ($\implies \Delta F >0$), so that upon a reduction in the pressure of the gas, the material will collapse and expel all residual gas to enhance the deliverable capacity compared to rigid materials that will retain some gas at $\pempty$. 
In addition, assume the open phase hosts a uniform, attractive potential energy field $\V<0$ for gas molecules to adsorb, so that eqn.~\ref{eq:xi_vs_xi0} holds for the open phase of the material.
In terms of $\rho_g(\mu, T)$, then, the grand potential $\Omega$ in our idealized substrate is:
\begin{equation}
    \Omega(T, \mu) = - \int_{-\infty}^\mu \rho_g(\mu-\V)d\mu.
\end{equation}
However, the \emph{osmotic potential} 
% David: introduce units of delta G here.
